\vspace{60pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-11 design.tex
Digging into social

  Elective courses can either be courses that are required for a major or minor, but are chosen by the student, or they can be courses of particular interest to students who have the flexibility to take them. For this use-case, Skedge offers search, filter, and sorting features that substantially aid users in browsing through courses and discovering ones they might want to take. Note that none of the following are supported by CDCS.

@@

    \item The Skedge DSQL includes the ``new'' keyword, which qualifies an accompanying search by only displaying the courses that were not offered the previous year for that term. For instance, searching ``new csc'' today (Fall 2016) would show Fall Computer Science courses that have been added to the catalog or changed since Fall 2015.
    \item The Skedge DSQL could include an ``autofit'' keyword, which would take into account the user's current schedule, and only show sections that would not conflict with any already scheduled times.\footnote{This feature is under development and is not currently live.}
    \item The Skedge DSQL includes the ``random'' keyword, which displays a single random course matching the accompanying query. For instance, ``random csc'' would show a random course in Computer Science for the current term. Used in conjunction with ``autofit'', it can a powerful way to find interesting new classes that are available for users to try.
    \item The Skedge DSQL includes sorting by class size---useful for students trying to find smaller, discussion based classes---or by class starting time---for students with preferences of morning or afternoon/evening classes.
    \item Because instructor names appearing in courses automatically link to searches for more courses taught by that instructor, it is easier and more natural to browse by instructor. [NEED STAT HERE]

@@

The question ``what are you taking this semester?'' may possibly be the most common phrase uttered in campus smalltalk within the first few weeks of a semester (as well as its analogue ``what are you taking \emph{next} semester?'' in the last half of a semester). I hypothesize that this question seeks to do the following:

\begin{itemize}
  \item Satisfy curiosity
  \item Find common courses
  \item Find common free time to meet
  \item Seek or solicit advice about courses
\end{itemize}

@@

\begin{figure}[ht]
  \centering
  \vspace{10pt}
  \includegraphics[width=6cm]{images/cdcs/social}
  \caption{Static image} \label{fig:cdcs-social}
\end{figure}

@@

    When this link is posted on Facebook, Skedge will include a rendered image of the schedule in the post, maintaining the element of visual bait with posting a static image.

    \begin{figure}[H]
      \centering
      \begin{tabular}{c c}
        \begin{subfigure}[w]{10.5cm}
          \centering
          \fbox{
            \includegraphics[width=1.00\textwidth]{images/skedge/share}
          }
          \caption{Skedge's schedule ``share'' page, publicly accessible at \url{http://skedgeur.com/1234}, with the last four digits being the randomly generated ID for that schedule. Hovering over a course shows information about it, and clicking searches for it.} \label{fig:sk-share}
        \end{subfigure} \vspace{15pt}\\

        \begin{subfigure}[w]{10.5cm}
          \centering
          \fbox{
            \includegraphics[width=1.00\textwidth]{images/skedge/share-compare}
          }
          \caption{The ``overlay'' feature enabled, superimposing the user's schedule over the share page's schedule.} \label{fig:sk-overlay}
        \end{subfigure}
      \end{tabular}
      \caption{Skedge's per-schedule share page}
    \end{figure}

@@

    \item typically only occurs for the \emph{current} semester. Under the Facebook model, it can be very difficult, nigh impossible, for students looking for opinions, tips, or even academic help for a specific class to find others who had taken that class before. 
  \end{enumerate}

@@

The \emph{Skedge Social} platform aims to leverage existing social media paradigms (such as the \emph{news feed}, \emph{likes}, and \emph{requests}) to more seamlessly give users answers to the questions alluded to earlier---``What are my friends taking?'' and ``What do my friends recommend?''. Skedge Social consists of the following several components:

  \subsubsection{One-click integration}

    Login

    \begin{figure}[H]
      \centering
      \fbox{
        \includegraphics[width=14cm]{images/skedge/social-login}
      }
      \caption{Skedge Social landing page for a user whose account has not yet been integrated with Facebook. Skedge Social appears in the context of the ordinary Skedge interface, and is accessible with the globe icon to the right of the searchbar.} \label{fig:sk-social-login}
    \end{figure}

  \subsubsection{Peer schedules}

  Mini-feed

    \begin{figure}[H]
      \centering
      \fbox{
        \includegraphics[width=10cm]{images/skedge/social}
      }
      \caption{Skedge Social's schedule feed (the default of four tabs) for a user who has integrated their Skedge account with Facebook.} \label{fig:sk-social}
    \end{figure}

  \subsubsection{Peer-liked courses}

  \subsubsection{Likes \& enrollments embedded in search results}

  ugh screenshot

>>>>

  Elective courses can either be courses that are required for a major or minor, but are chosen by the student, or they can be courses of particular interest to students who have the flexibility to take them. For this use-case, Skedge offers search, filter, and sorting features that substantially aid users in browsing through courses and discovering ones they might want to take. Note that none of the following features are supported by CDCS.

@@

    \item The Skedge DSQL includes the ``new'' keyword, which qualifies an accompanying search by only displaying the courses that were not offered the previous year for that term. For instance, searching ``new csc'' today (Fall 2016) would show Fall Computer Science courses that have been added to the catalog or changed since Fall 2015.
    \item The Skedge DSQL could include an ``autofit'' keyword, which would take into account the user's current schedule, and only show sections that would not conflict with any already scheduled times.\footnote{This feature is under development and is not currently live.}
    \item The Skedge DSQL includes the ``random'' keyword, which displays a single random course matching the accompanying query. For instance, ``random csc'' would show a random course in Computer Science for the current term. Used in conjunction with ``autofit'', it can a powerful way to find interesting new classes that are available for users to try.
    \item The Skedge DSQL includes sorting by class size---useful for students trying to find smaller, discussion based classes---or by class starting time---for students with preferences of morning or afternoon/evening classes.
    \item Instructor names appearing in courses automatically link to searches for more courses taught by that instructor, which is easier than having to use the CDCS ``instructor'' field to make a separate search.

@@

The question ``what are you taking this semester?'' may possibly be the most common phrase uttered in campus smalltalk within the first few weeks of a semester (as well as its analogue ``what are you taking \emph{next} semester?'' in the last half of a semester).

@@

\begin{figure}[H]
  \centering
  \vspace{5pt}
  \begin{tabular}{c c}

    \begin{subfigure}[w]{7cm}
      \centering
      \includegraphics[width=6.5cm]{images/cdcs/social}
      \caption{Sharing a static schedule image generated by Better CDCS on Facebook} \label{fig:cdcs-social}
    \end{subfigure}

    \hspace{10pt}

    \begin{subfigure}[w]{7.1cm}
      \centering
      \includegraphics[width=6.6cm]{images/skedge/facebook}
      \caption{Sharing a Skedge schedule on Facebook, linked to the live and dynamic schedule share page on Skedge} \label{fig:sk-fb}
    \end{subfigure}

  \end{tabular}
  \caption{Comparison of sharing schedules on Facebook}
\end{figure}

@@

    When this link is posted on Facebook, Skedge will include a rendered image of the schedule in the post, maintaining the element of visual bait with posting a static image (see Figure \ref{fig:sk-fb}).

    \begin{figure}[H]
      \centering
      \begin{tabular}{c c}
        \begin{subfigure}[w]{11cm}
          \centering
          \fbox{
            \includegraphics[width=1.00\textwidth]{images/skedge/share}
          }
          \caption{Skedge's schedule ``share'' page, publicly accessible at \url{http://skedgeur.com/1234}, with the last four digits being the randomly generated ID for that schedule. Hovering over a course shows information about it, and clicking searches for it.} \label{fig:sk-share}
        \end{subfigure} \vspace{25pt}\\

        \begin{subfigure}[w]{11cm}
          \centering
          \fbox{
            \includegraphics[width=1.00\textwidth]{images/skedge/share-compare}
          }
          \caption{The ``overlay'' feature enabled, superimposing the user's schedule over the share page's schedule.} \label{fig:sk-overlay}
        \end{subfigure}
      \end{tabular}
      \caption{Skedge's per-schedule share page}
    \end{figure}

@@

    \item typically only occurs for the \emph{current} semester. Under the Facebook model, it can be very difficult, nigh impossible, for students seeking advice, opinions, or even academic help for a specific class to find others who had taken that class before.
  \end{enumerate}

@@

The \emph{Skedge Social} platform aims to leverage existing social media paradigms (such as the \emph{news feed}, \emph{likes}, and \emph{requests}) to more seamlessly give users answers to the questions alluded to earlier---``What are my friends taking?'' and ``What do my friends recommend?''.

Logging into Skedge Social is very simple---if the user is already logged into Facebook, it just requires one button of authorization (see Figure \ref{fig:sk-social-login}).

  \begin{figure}[H]
      \centering
      \fbox{
        \includegraphics[width=9cm]{images/skedge/social-login}
      }
      \caption{Skedge Social landing page (\url{http://skedgeur.com/social}) for a user whose account has not yet been integrated with Facebook. Skedge Social appears in the context of the ordinary Skedge interface, and is accessible with the globe icon to the right of the searchbar.} \label{fig:sk-social-login}
    \end{figure}

  \subsubsection{Schedule feed}

  Immediately after logging in, the user will see the ``schedule feed,'' the list of the user's peers' current schedules. This takes from a familiar paradigm of the \emph{feed} in social networks, which is routinely scrolled for updates. For each schedule in the feed, the user can easily visualize their own schedule side-by-side (using with the same ``overlay'' mechanic explained earlier), access the Facebook profile of the schedule's owner, and see the list of that users' course like.

    \begin{figure}
      \centering
      \fbox{
        \includegraphics[width=10cm]{images/skedge/social}
      }
      \caption{Skedge Social's schedule feed (the default of four tabs) for a user who has integrated their Skedge account with Facebook. The user can toggle between a peer's schedule and the list of their \emph{liked} courses.} \label{fig:sk-social}
    \end{figure}

  \subsubsection{Search result integration}

  Skedge Social also integrates into course search results, showing users on the platform their Facebook friends who are taking, have taken, or \emph{liked} each particular course (see Figure \ref{fig:sk-social-course}). This has several advantages:

  \begin{itemize}

  \item It enhances the user's social engagement and allows them to better keep up with peers.
  \item It promotes and facilitates communication for users either seeking or soliciting advice regarding courses (sending a Facebook message is merely two clicks away).
  \item It brings attention to courses which are particularly popular or liked among the user's community of peers, increasing the chances of serendipitous course discovery.

  \end{itemize}

    \begin{figure}[H]
      \centering
      \fbox{
        \includegraphics[width=12cm]{images/skedge/social-course}
      }
      \caption{Skedge Social integrating into a course search result} \label{fig:sk-social-course}
    \end{figure}
